\Large\bf FlexibleSUSY --- A spectrum generator generator for supersymmetric models

### 2014-10-30 doc/flexiblesusy-paper.tex
simplify statement about slhaea.

The standard input and output of the generated code is given in
SLHA-style format where the user has control of the Block names by
editing the SARAH files and may also add extra blocks in the
FlexibleSUSY.m model file which is decribed in section 5. We use the
well known SLHAea \cite{slhaea} to create these SLHA files and with a
simple modifications these can be passed directly to another code
which uses them as an alternative to writing out the SLHA file. Since the
SLHA standard is intended precisely for the purpose, MSSM and NMSSM
codes should be compliant with this.  We have tested that the versions
of HDECAY\cite{hdecay} and SDECAY\cite{sdecay} inside SUSY-HIT
\cite{susyhit} can understand the SLHA output of FlexibleSUSY and give
matching output to that from SOFTSUSY.

>>>>

The standard input and output of the generated code is given in
SLHA-style format where the user has control of the Block names by
editing the SARAH files and may also add extra blocks in the
FlexibleSUSY.m model file which is decribed in section 5. We use
SLHAea \cite{slhaea} to create these SLHA files and with a simple
modifications these can be passed directly to another code which uses
them as an alternative to writing out the SLHA file. Since the SLHA
standard is intended precisely for the purpose, MSSM and NMSSM codes
should be compliant with this.  We have tested that the versions of
HDECAY\cite{hdecay} and SDECAY\cite{sdecay} inside SUSY-HIT
\cite{susyhit} can understand the SLHA output of FlexibleSUSY and give
matching output to that from SOFTSUSY.
